High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-21 doc/asplos2013/intro.tex
Small edits to the intro

\item We describe a physical region system for the management of data that abstracts
data layouts.  Abstracted data layouts enable composable reduction operations that can be
deferred to further hide latency (Section~\ref{subsec:phyreg}).

@@

Finally, Section~\ref{sec:related} describes related work and in Section~\ref{sec:conclusion}
concludes.

>>>>

\item We describe a physical region system that provides structural information about
data layout.  The structural information provided by physical regions enables an extensible
interface for conjoining operations and transformations with asynchronous data movement for 
further lantecy hiding (Section~\ref{subsec:phyreg}).

@@

Section~\ref{sec:related} describes related work and Section~\ref{sec:conclusion}
concludes.
